\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
remove whitespace
edits and comments

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map.

@@

\subsubsection{The Need for an Editor}

@@

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely
Japanese. While AR translation apps exist, the experience can be frustrating,
and produce poor results. Google's text recognition and machine-learning
powered translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant''
mode. In ``instant'' mode, the app attempts to translate text as quickly as
possible and superimpose the translated text onto the real world using the
camera. In ``scan'' mode, the user takes a photo. Then, the user is prompted
to highlight where text appears in the photo. After the translation is
complete, the translated text appears in a separate UI element instead
superimposed onto the photo. In most cases, it is more convenient and
readable to have the translation appear in a separate scrollable textbox.
This motivated the current design of the ``info buttons'' in ARuko. Instead
of placing text directly onto signage, we place a blue button with an `i' in
the center. By tapping on this button, a separate UI element will appear
containing the translated text. Since this button is cast into the world
using the AR camera, the button is intuitively placed directly onto the
content in the real world.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane
of the ticket, sitting on the paper as if it were ground. Atticus suggested
that we re-orient the model such that the ticket served as a back plane. This
would allow users to hold the ticket vertically, and view the Golden Pavilion
floating in front of the ticket. This would allow users to place their hands
under the base of the Golden Pavilion model as if they were holding it.
Vuforia's image tracking is flexible enough such that the image target can be
partially obscured.

@@

The inclusion of a ``chapter selection'' screen had other notable design
implications as well. Initially different regions were triggered solely by your
GPS location. Walking into a region would prompt the available images to change
on screen. Also, a new audio track would begin to play. This forced us to
answer certain basic questions about the chapter select screen for ourselves.
For example, consider a user that steps into one region, triggering the audio
and images. Then, that user selects a chapter from the chapter selection menu,
overriding the ``true'' region the user is physically standing inside of. When
does the GPS ``take over'' again? Should the region change back to the ``true''
region once the audio of the selected region finishes? This might be intuitive
and preferred for most users, but what if the user is more interested in the
image gallery than the audio? Then, the persistence of the image gallery is
strangely tied to the duration of the audio track playing underneath. What if a
user selects a chapter, and then physically enters that region moments later?
Should the audio restart to indicate that the user has arrived at the location?
Or, will this appear as though the audio track the user was already listening
to skipped to the beginning again for no reason? As you can imagine, this
seemingly minor inclusion created a significant amount of discussion.

@@

Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

@@

Because the Editour is intended only to be a tool to aid Atticus in creating
tours our user testing was less rigid. Even so, the frontend and backend we
built for Editour ended up being largely reliable. The main source of
reliability issues stemmed from the hosting provider, which was out of our
control.

@@

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} should make it clear why
this works. This algorithm's time complexity is $O(n)$, where $n$ is the sum
total of the number of vertices of all of the polygons being
tested~\autocite{geeksforgeekspolygon}.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. The region at the bottom surrounding our dormitories was added
for our convenience, allowing us to test the app while we were away from the
lab.  As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.

@@

Our first day of on-site testing with the app took place on September
6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
Atticus already created. The first version of the rebuilt tour had regions that
were relatively small; some regions were only a few meters across. This version
of the tour can be seen in Figure~\ref{fig:kinkakujiTour}.

@@

Our previous testing involved creating a ``mock tour'' on the Ritsumeikan
campus. While this let us know generally which features of the app were working,
it was very difficult to know how ahead of time how well our app would work at
Kinkaku-ji.

@@

Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
app is not fully functional on a phone that old. At the same time, it was
informative to take both phones through the tour. Initially, we made the design
decision to update the GPS location every 60 frames. On a phone running the app
at full speed, this should happen once every second. Because the Samsung Galaxy
S7 was having trouble running the app at full speed, the GPS updated far less
frequently. This was an oversight that would have been difficult to catch if we
had not tested on hardware below the recommended specifications.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met
up with Atticus, the IQP group, and our friend Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how
the app works we had each of them try going through Kinkaku-ji while
listening to the tour and using the app's features. Each member of our team
also installed the beta version so we could fuzz test it.

@@

Similarly, we noticed that we were only able to augment a maximum of two
image targets at a time. In almost all cases, only two translatable signs
were in view at once. The only scenario in which there were more than two
image targets in view at a given time was with the four framed photos of the
interior, arranged in a two by two grid. When standing at a distance from the
grid, only two images would be augmented with the blue information button. By
default, Vuforia limits the amount of image targets that the engine should
accept simultaneously. In the Vuforia engine settings, we changed this limit
to accommodate for four simultaneous images

>>>>

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map, edit those regions and assign media to each of
the drawn regions.

@@

\subsubsection{The Need for an Editor}
\label{sec:theNeedForAnEditor}

@@

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely Japanese.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. Then, the user is prompted to
highlight where text appears in the photo. After the translation is complete,
the translated text appears in a separate UI element instead superimposed onto
the photo. In most cases, it is more convenient and readable to have the
translation appear in a separate scrollable textbox. This motivated the current
design of the ``info buttons'' in ARuko. Instead of placing text directly onto
signage, we place a blue button with an `i' in the center. By tapping on this
button, a separate UI element will appear containing the translated text. Since
this button is cast into the world using the AR camera, the button is
intuitively placed directly onto the content in the real world.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground. Atticus suggested that
we re-orient the model such that the ticket served as a back plane. This would
allow users to hold the ticket vertically, and view the Golden Pavilion
floating in front of the ticket. This allows users to place their hands under
the base of the Golden Pavilion model as if they were holding it. Vuforia's
image tracking is flexible enough such that the image target can be partially
obscured.

@@

The inclusion of a ``chapter selection'' screen had other notable design
implications as well. Initially different regions were triggered solely by the
GPS location. Walking into a region would prompt the available images to change
on screen. Also, a new audio track would begin to play. This forced us to
answer certain basic questions about the chapter select screen for ourselves.
For example, consider a user that steps into one region, triggering the audio
and images. Then, that user selects a chapter from the chapter selection menu,
overriding the ``true'' region the user is physically standing inside of. When
does the GPS ``take over'' again? Should the region change back to the ``true''
region once the audio of the selected region finishes? This might be intuitive
and preferred for most users, but what if the user is more interested in the
image gallery than the audio? Then, the persistence of the image gallery is
strangely tied to the duration of the audio track playing underneath. What if a
user selects a chapter, and then physically enters that region moments later?
Should the audio restart to indicate that the user has arrived at the location?
Or, will this appear as though the audio track skipped to the beginning again
for no reason? As you can imagine, this seemingly minor inclusion created a
significant amount of discussion.

@@

%TODO should this paragraph move somewhere else?
Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

@@

Because the Editour is intended only to be a tool to aid Atticus in creating
tours our user testing was less rigid. Even so, the frontend and backend we
built for Editour ended up being largely reliable. The reliability issues
stemmed from the hosting provider, which was out of our control.

@@

One decent algorithm for accomplishing this is by drawing a ray from a given
point to infinity. Barring edge cases (which will be discussed shortly) the
point is inside the polygon if the ray passes through an even number of line
segments.  The point is outside of the polygon if the ray intersects an odd
number of times. Figure~\ref{fig:intersectionsDiagram} does not serve as a
proof, but should at least make it clear why this works. This algorithm's time
complexity is $O(n)$, where $n$ is the sum total of the number of vertices of
all of the polygons being tested~\autocite{geeksforgeekspolygon}.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This uniquely shaped region also prompted us to think about
what UI behavior made the most sense if a user were to walk into a region, walk
out and then in again. We decided that it was awkward if the audio restarted
upon re-entering a region, since the audio would still be playing once a user
left the region. (The region at the bottom surrounding our dormitories was added
for our convenience, allowing us to test the app while we were away from the
lab.) As we began to implement more complex UI that changed based on GPS
position in various ways, directly taking the tour by walking around was an
invaluable way to test. Section~\ref{sec:adobeXdDesign} details how the UI grew
in complexity in the late stages of the project. Having a way to regularly run
field tests was integral to polishing the app in time before we revisited
Kinkaku-ji.  Because the Editour was flexible enough to easily swap out media
and add regions to the tour, the Editour proved itself to be as helpful for
testing as it was for crafting the final tour that could be taken at
Kinkaku-ji.

If we were ever feeling too tired to test the app by walking around, we also
mocked the GPS coordinates in software. This allowed us to simulate walking in
a single direction without actually having to move or build to a mobile device.

@@

Our first day of on-site testing with the app took place on September
6\textsuperscript{th}. Using Editour, we rebuilt the izi.TRAVEL audio tour that
Atticus already created. The first version of the rebuilt tour had regions that
were relatively small; some regions were only a few meters across. This version
of the tour can be seen in Figure~\ref{fig:kinkakujiTour}. This day of testing
prior to the redesign discussed in Section~\ref{sec:adobeXdDesign}.

@@

As discussed in Section~\ref{sec:testingARuko}, our previous testing involved
creating a ``mock tour'' on the Ritsumeikan campus. While this let us know
generally which features of the app were working, it was very difficult to know
how ahead of time how well our app would work at Kinkaku-ji.

@@

Initially, we loaded the app onto the Samsung Galaxy S7 as a backup, since the
AR features were not fully functional on a phone that old. At the same time, it
was informative to take both phones through the tour. Initially, we made the
design decision to update the GPS location every 60 frames. On a phone running
the app at full speed, this should happen once every second. Because the
Samsung Galaxy S7 was having trouble running the app at full speed, the GPS
updated far less frequently. This was an oversight that would have been
difficult to catch if we had not tested on hardware below the recommended
specifications.

@@

On September 26\textsuperscript{th} we returned to Kinkaku-ji with a nearly
complete version of the ARuko in order to conduct some final testing. We met
up with Atticus, the IQP group, and our friend Hikaru and installed the beta
version of ARuko on each of their phones. With little instruction about how
the app works we had each of them try going through Kinkaku-ji while
listening to the tour and using the app's features. Each member of our team
also installed the beta version so we could fuzz test it.
% TODO check if fuzz testing is really the right word here

@@

We also noticed that we were only able to augment a maximum of two
image targets at a time. In almost all cases, only two translatable signs
were in view at once. The only scenario in which there were more than two
image targets in view at a given time was with the four framed photos of the
interior, arranged in a two by two grid. When standing at a distance from the
grid, only two images would be augmented with the blue information button. By
default, Vuforia limits the amount of image targets that the engine should
accept simultaneously. In the Vuforia engine settings, we changed this limit
to accommodate for four simultaneous images
